Supplemental Information

### 2024-11-17 paper/supplemental_information.Rmd
bug fix and further development

```{r, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE)
```

```{r}
knitr::purl("paper.Rmd", documentation = 0)
source("paper.R")
```

# Supplemental Figure 1: Age histograms

@@

# Supplemental Table 1: Model comparison for accuracy models

@@

# Supplemental Table 2: Model comparison for reaction time models

@@

# Supplemental Table 3: Reliabilities by dataset

@@

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(here)
source(here("helper","common.R"))
```

```{r, echo=FALSE}
knitr::purl("paper.Rmd", documentation = 0)
suppressMessages(source("paper.R"))
```

# Dataset description

@@

```{r, fig.cap="Number of administrations for datasets with repeated measurements."}
longitudinal <- d_sub |>
  group_by(dataset_name, subject_id) |>
  count() |>
  filter(n > 1)

d_sub_long <- d_sub |>
  filter(subject_id %in% longitudinal$subject_id) |>
  group_by(subject_id) |>
  arrange(age) |>
  mutate(admin_num = 1:n(), 
         delta_t = age - age[1])

ggplot(d_sub_long, 
       aes(x = delta_t, fill = dataset_name)) +
  geom_histogram(binwidth = 1) + 
  # facet_wrap(~dataset_name) + 
  xlab("Age since first test")
```

# Speed and accuracy

Correlations between variables

```{r, results = "asis"}

cor(select(d_sub, age, log_age, rt, log_rt, 
           long_window_accuracy, short_window_accuracy, prod, comp), 
    use = "pairwise.complete.obs") |>
  round(2) |>
  papaja::apa_table()

```

@@

@@

# Exploratory Factor Analysis

- Full EFA results

# Alternative Factor Structures

- Alternative factor models: variances together, two factor, etc. etc.

# Sensitivity Analysis for Longitudinal Models

THIS IS WRONG

@@

Sensitivity analysis for age split point (e.g., split at 3 months)

Sensitivity analysis for measurement invariance (e.g., not constraining loadings)

# Analyses using short window accuracy

## Longitudinal factor analysis

## Longitudinal factor analysis
